---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# quick.boxplot

<!-- badges: start -->
<!-- badges: end -->

The goal of quick.boxplot is to create a quick ggplot2 boxplot from a categorical and continous variable. 

## Installation

quick_boxplot is not availabe on CRAN, but you can download with: 

``` r
install.packages("quick.boxplot")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mchester/assignment_b2")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(quick.boxplot)
quick_boxplot(datateachr::cancer_sample, diagnosis, area_mean)
quick_boxplot(gapminder:: gapminder, continent, lifeExp)
```

This package is special it saves you from repeating code in the visualization of the difference of means between categorical and continuous variables. 
